### 2022-06-24 pv_evaluation/templates/inventor/0-report.qmd
update

This is report has been automatically generated for the following data sources:

- **Disambiguation summary tables:**
{% for filename in summary_table_files %}
    - {{ filename }}
{% endfor %}

>>>>

This is report has been automatically generated for the following data source(s) at {{ datetime }}:

{% for filename in summary_table_files %}
- {{ filename }}
{% endfor %}
